Directly inferring Distances and Physical Properties of stellar system using Simulation Based Inference

### 2023-12-13 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Constraining the Distances and Physical Properties of Semiresolved Galaxies with Simulation Based Inference}

@@

\section{The \code{} Framework}
\subsection{Simulating images Dwarf Galaxies}
\label{sec:sfh}
To simulate dwarf galaxies we utilize the \artpop{} pacakge. \artpop{} generates artificial images of dwarf galaxies ``from the ground up" by drawing stellar masses from an IMF, calculates luminosities using isochrones, draws positions for each start using a pre-defined brightness profile and then directly injects stars into an image before convolving with the PSF.

@@

\section{Inference on a Mock Galaxy}
\label{self-test}
Talk about performing inference on a simulated galaxy. Show recovered posteriors along with SBC benchmarks showing a well behaved posterior

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/Pal4_post_corner.pdf}
    \includegraphics[width=0.45\textwidth]{figures/Pal13_post_corner.pdf}
    \includegraphics[width=0.4\textwidth]{figures/Pal4_ims_post.pdf}
    \hspace{1cm}
    \includegraphics[width=0.4\textwidth]{figures/Pal13_ims_post.pdf}
    \caption{Caption}
    \script{plot_gc.py}
    \label{fig:Pal4}
\end{figure*}

\subsection{Dwarfs in the Sculptor Group}
\label{sec:scul}
\subsection{Galaxies in HSC}
\label{sec:hsc}

>>>>

% Title
\title{Directly inferring Distances and Physical Properties of stellar system using Simulation Based Inference}

@@

\section{The \code{}\ Framework}
\subsection{Simulating images Dwarf Galaxies}
\label{sec:sfh}
To simulate dwarf galaxies we utilize the \artpop{} pacakge. \artpop{} generates artificial images of dwarf galaxies ``from the ground up" by drawing stellar masses from an IMF, calculates luminosities using isochrones, draws positions for each start using a pre-defined brightness profile and then directly injects stars into an image before convolving with the PSF.

@@

\section{Inference on a Mock Galaxy}
\label{sec:self-test}
\begin{figure*}
    \centering
    \includegraphics[width = 0.8\textwidth]{figures/self_test_post_corner.pdf}
    \includegraphics[width = 0.8\textwidth]{figures/self_test_ims.pdf}
    \caption{Plotting the results of a simple injection-recovery test. Seems to be pretty good although it is a little too confident about the stellar population parameters}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_post}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width = 0.95\columnwidth]{figures/self_test_sbc.pdf}
    \caption{Plotting the results of a simple injection-recovery test. Seems to be pretty good although it is a little too confident about the stellar population parameters}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_sbc}
\end{figure}

Talk about performing inference on a simulated galaxy. Show recovered posteriors along with SBC benchmarks showing a well behaved posterior

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/Pal4_post_corner.pdf}
    \includegraphics[width=0.45\textwidth]{figures/Pal13_post_corner.pdf}
    \includegraphics[width=0.4\textwidth]{figures/Pal4_ims_post.pdf}
    \hspace{1cm}
    \includegraphics[width=0.4\textwidth]{figures/Pal13_ims_post.pdf}
    \caption{Caption}
    \script{plot_gc.py}
    \label{fig:GCs}
\end{figure*}

\subsection{Dwarfs in the Sculptor Group}
\label{sec:scul}

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/ESO_294_10_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_294_10_ims_post.pdf}
    \includegraphics[width=0.5\textwidth]{figures/ESO_410_05_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_410_05_ims_post.pdf}
    \caption{Caption}
    \script{plot_scul_dw.ipynb}
    \label{fig:sdw_2mpc}
\end{figure*}

\subsection{Galaxies in HSC}
\label{sec:hsc}
